---
title: "Process"
drake_cache: ".HW7step2"
output: html_document
params:
  title: "HW7" # google classroom上公告作業時所用的標題
  ansfilename: "homeworks/homework7-ans.Rmd"
  submissionFolder: "studentsSubmission"
  gradingFolder: "grading_flow"
---

```{r setup, include=FALSE, drake=F}
knitr::opts_chunk$set(echo = TRUE, eval=F)
library(drake)
library(econDV)
library(dplyr)

```

## makecondition

```{r makecondition}
library(drake)
library(rmd2drake)
library(dplyr)
library(googleclassroom)
library(readr)
library(rmdgrader)
library(purrr)
library(rlang)
library(testthat)
library(withr)
rprojroot::is_rstudio_project$make_fix_file() -> .root
.root <- function(){
  "/Users/martinl/Github/course-dashboard-programming-for-data-science"
}
problemFolder <-
  file.path(.root(), params$submissionFolder, params$title,
            "problem")
```


## Process

```{r processing}
# initiate process instance
process <- Process()
# get list of code chunks
process$correctAnsFilename$tryGet_list_codeChunks()
process$inBatch_studentsRmds$tryGet_list_codeChunks()

# If one Rmd content changed, you can update simply that student's respective elements in process instance like:
# process$studentsRmds$HW8_410672033.Rmd$tryGet_list_codeChunks()
```


## Evaluate

After users get list_codeChunks from all Rmd files, it's time to evaluate these codes. 

```{r evaluation}
# Initiate an Evaluation Instance
ei <- Evaluate(process)

# resolve codes in batch
ei$answerValues$batch$resolve$part4()
ei$answerValues$batch$resolve$part5()
# once resolved, answer values will show up for all Rmds such as:
ei$answerValues$HW7_410672033.Rmd$values
```

```{r}
process$file.edit$HW7_410874206.Rmd()
process$studentsRmds$HW7_410874206.Rmd$move2problem()
```

### when screwed

Sometimes students throwed in, say totally wrong Rmd, it can break down batch evaluation. In this case, run the follow example code (which uses part4) as an example.

```{r}
for(.it in seq_along(ei$allRmds)){
  cat(glue::glue('{ei$allRmds[[.it]]}\n\n'))
  ei$answerValues[[ei$allRmds[[.it]]]]$resolve$part4()
}
```

The loop stops at where the problem from, say HW7_410874206.Rmd. Then you can use the move2problem method to remove it. Just remember to do .nullify after each removal.

```{r}
process$studentsRmds$HW7_410874206.Rmd$move2problem()
process$.nullify()
```

process is actually equip with file.edit method. Use it like:
```{r}
process$file.edit$HW7_410672056.Rmd()
```

Once done, you can restart a new Evaluation instance (no need to start from Process stage).

### individually

```{r}
# You can also evaluate each Rmd codes one-by-one via their own resolve method. Once resolved, you can see the values after resolution
ei$answerValues$`homework7-ans.Rmd`$resolve$part4()
ei$answerValues$`homework7-ans.Rmd`$resolve$part5()
ei$answerValues$`homework7-ans.Rmd`$resolve$part6()
View(ei$answerValues$`homework7-ans.Rmd`$values)
```



## Save
You only save neccessary answer values for grading step via save method.

```{r}
ei$save(filename = "data4step3.Rdata")
```

