---
title: "homework 8"
output: html_document
params:
  studentName: "你的名字"
  studentID: "你的學號"
---

> 每次作業滿分10分：有寫作業於期限內上傳得3分，剩餘7分依作業準確率決定最後得分多寡，除非該題另有規定。

> 前述存檔與frontmatter要求缺任何一個則扣1分。

## 成績

```{r grade}

df_grade <- 
jsonlite::fromJSON('[{"grade":1,"comment":"","_row":"ans12.1"},{"grade":0.9,"comment":"在lowerTriX賦值時出了小錯。","_row":"ans12.2"},{"grade":0.9,"comment":"雖然有計算小錯誤，但程式架構清楚，瑕不掩瑜。","_row":"ans12.3"},{"grade":1,"comment":"","_row":"ans13.1s"},{"grade":0,"comment":"","_row":"ans13.2s"}]')
totalGrade <- list()
within(
  totalGrade,
  {
    rawGrade = sum(df_grade$grade)
    finalGrade = rawGrade/nrow(df_grade)*7+3
  }
) -> totalGrade
print(df_grade)
print(totalGrade)
        ans <- new.env(parent=.GlobalEnv) #對答案用

```


請先執以下code chunk, 引入所需packages，答案禁止引用其他套件（Package）。

```{r setup}
knitr::opts_chunk$set(echo = F, eval=F)
library(jsonlite); library(lubridate); library(readr); library(stringr); library(purrr); library(glue)
```

# 題目

完成第5章綜合練習以下幾題：

### 12. Subscripts {.unnumbered}

#### 12.1 Dimension aspect {.unnumbered}

```{r data12.1}
set.seed(5928)
n <- sample(3:7, 1) 
sampleMatrix <- matrix(sample(1:100, n^2), n, n)
sampleMatrix
```

```{r ans12.1}
# obtain the diagonal elements

# 任務前提
n <- dim(sampleMatrix)[[1]]
diagX <- vector("numeric", n)
# 任務目標: 縮小任務，只一個i值, 
for (i in 1:n) {
  diagX[[i]] <- sampleMatrix[i,i]
}

diagX

# diagX


#' 參考解答 ------------------

{
# 任務前提
n <- dim(sampleMatrix)[[1]]
diagX <- vector("numeric", n)
# 任務目標: 縮小任務，只一個i值, 
for(i in 1:n)
{
  diagX[[i]] <- sampleMatrix[i,i]
}
  
# diagX
} %at% ans
```

#### 12.2 Lower triangular dimension {.unnumbered}

```{r ans12.2}
# extract the lower triangular elements
# j <= i

# 任務前提
n <- dim(sampleMatrix)[[1]]
lowerTriX <- vector("list", n)
# 任務目標(縮小版): i <- 3，找出所有x_{3j}, where j <= 3

for (i in 1:n) {
  # 找出所有比i小的j所對應的sampleMatrix[1,j]值，再把需要重複的1代換成i
  for (j in 1:n) {
    if(j<=i){
      lowerTriX[[i]][[j]] <- sampleMatrix[i,j]
    }
  }
}

# lowerTriX


#' 參考解答 ------------------

{
# 任務前提
n <- dim(sampleMatrix)[[1]]
# 任務目標(縮小版): i <- 3，找出所有x_{3j}, where j <= 3
lowerTriX <- vector("list", n)
for(i in 1:n){
  lowerTriX[[i]] <- vector("numeric", i)
  for(j in 1:i)
  {
     lowerTriX[[i]][[j]] <- sampleMatrix[i,j]
  }
}

# lowerTriX
} %at% ans
```

#### 12.3 Covariate columns {.unnumbered}

```{r data12.3}
simData <- data.frame(
  district=rep(LETTERS[1:3], each=3),
  year=rep(seq(1990, 2000, by=5), 3)
)
simData$income <- {
  sample(2000:10000, 3) -> .i
  unlist(purrr::map(.i, 
      ~{
        .x+sample(-500:500,3)
      }))
}
simData
```

Compute mean income (average across three years) of every district using for-loop and save them in **meanIncomes**. You may adopt the following template:

```{r ans12.3}
# Compute mean income (average across three years) of every district 
# 任務前題
districtSet <- unique(simData$district)
meanIncomes <- numeric()
yearSet <- unique(simData$year)
totalincome <- vector("numeric", length(districtSet))

# 各地區三年平均收入
for (d in districtSet) {
  # 單一地區三年平均收入
  meanIncomes[[d]] <- {
    #三年總收入
    for (y in yearSet) {
      totalincome[[1]] <- totalincome[[1]] + simData$income[which(simData$district==d & simData$year==y)]
    }
    # 三年平均收入
    totalincome[[1]]/length(yearSet)
  }
}

# meanIncomes


#' 參考解答 ------------------

{
# 任務前題
districtSet <- unique(simData$district)
meanIncomes <- vector("numeric", length(districtSet))
# 任務目標（縮小版）：找出districtSet[[1]]的（三年）平均所得
for(.x in 1:3)
{
  meanIncomes[[.x]] <- mean(simData$income[
    which(simData$district==districtSet[[.x]])
  ])
}
  
# meanIncomes
} %at% ans
```

### 13. Loop practices {.unnumbered}

#### 13.1 Three errors {.unnumbered}

```{r ans13.1s}
## 任務前提
realPassword <- "2ofe83"

## 一次性任務目標: 接受(flag_continuation為F) 或不接受userInput(flag_continuation為T)
.x <- 0
flag_continuation <- T

while(flag_continuation)
{
  # iterate generation
  .x <- .x+1 
  # for each iterate, you iteration block
    userInput <- 
      readline("Please input your password ")
    result <-
    # match "Password correct"
    if(userInput==realPassword){
      "Password correct"
    } else
    # not match "The password is wrong" and go back to ask to input
    if(userInput!=realPassword && .x<=3){
      "The password is wrong"
    } else
    # 3 times errors "You have input wrongly 3 times!" and exit
    {
      stop("You have input wrongly 3 times!")
    }
  message(result)
  # continuation flag generation (update)
  flag_continuation <- !str_detect(result, "correct")
}


#' 參考解答 ------------------

{
## 任務前提
realPassword <- "2ofe83"

.x <- 0
flag_continuation <- T
maxIt <- 3
while(flag_continuation && .x <= maxIt){
  ## 多次性任務目標: 接受(flag_continuation為F) 或不接受userInput(flag_continuation為T)
  .x <- .x + 1
  
  userInput <- readline("Please input your password ")
  
  flag_wrongInput <- userInput!=realPassword
  flag_reachMaxIt <- .x >= maxIt
  flag_continuation <- flag_wrongInput
  
  if(flag_wrongInput) {
    message("The password is wrong.\n")
    if(flag_reachMaxIt){
      cat("You have input wrongly 3 times!\n")
      flag_continuation <- F
    } 
  } else {
    message("Password correct.")
    flag_continuation <- F
  }
}
} %at% ans
```

#### 13.2 Password setup {.unnumbered}

```{r ans13.2s}
.x <- 0
flag_continuation <- T
maxIt <- 5
while(flag_continuation && .x <= maxIt)
{
  # iterate generation
  .x <- .x+1
  # iteration block
    userInput <- readline("Input your password ")
    result <- paste0(
      if(!(is.character(userInput) && str_count(userInput)>=6 && str_count(userInput)<=10))
      {"password should contain 6-10 characters\n"},
      if(!str_detect(userInput, "[:digit:]+"))
      {"Need at least one number\n"},
      if(!str_detect(userInput, "[:lower:]+"))
      {"Need at least one small case letter\n"},
      if(!str_detect(userInput, "[:upper:]+"))
      {"Need at least one capital letter\n"}
    )
    message(result)
    
  
  # continuation flag update (generation)
  flag_continuation <- !is_empty(result)
}


#' 參考解答 ------------------

{
.x <- 0
flag_continuation <- T
maxIt <- 5
while(flag_continuation && .x < maxIt)
{
  # iterate generation
  .x <- .x+1
  
  # iteration block
  {
    # undebug(hijack_readline2)
    userInput <- readline("Input your password ")
    flag_rule1 <- stringr::str_length(userInput)<6 || stringr::str_length(userInput)>10
    flag_rule2 <- !stringr::str_detect(userInput, "[0-9]+")
    flag_rule3 <- !stringr::str_detect(userInput, "[a-z]+")
    flag_rule4 <- !stringr::str_detect(userInput, "[A-Z]+")
    if(flag_rule1)
    {
      message("password should contain 6-10 characters")
    }
    if(flag_rule2)
    {
      message("Need at least one number")
    }
    if(flag_rule3)
    {
      message("Need at least one small case letter")
    }
    if(flag_rule4)
    {
      message("Need at least one capital letter")
    }
    
  }
  
  # continuation flag update (generation)
  flag_continuation <- (flag_rule1 || flag_rule2 || flag_rule3 || flag_rule4)
  
}
} %at% ans
```
