---
title: "rmdgrader 使用說明"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rmdgrader 使用說明}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=F
)
```

## Installation

```{r}
devtools::install_github("tpemartin/rmdgrader", force=T)
```

## Usage

```{r setup}
library(rmdgrader)
```

**rmdgrader** is a package that works with Google classroom and Google drive. It consists of:

1.  Exam Rmd template: The template to follow for **rmdgrader** to work.

2.  Download: Download student's Rmd file submission from a Google Drive folder

3.  Process: Extract Rmd code lines and restructure them according to questions

4.  Evaluate: Generate answer value objects for grading purpose.

5.  Grading: The stage of comparing students' answer value with correct answer value, and assigning grade by grouped comparing results.

6.  Sythesize: Adding student's grading result to his Rmd file for returning.

7.  Inspection: Manually inspect student's synthesized Rmd, change its grade and update grade


## Exam design

**File** > **New File** > **R Markdown...**  

Click **From Template**, select **Exam Rmd**, click **OK**.

Design your exam with answers and save the file as `XXXX - ans.Rmd`. Then from **Addins** > **extract exercise Rmd from ans Rmd**, it will generate an `XXXX.Rmd` that has the same Rmd content as `ans.Rmd` but with all the content inside `ansXXX` code chunk cleaned. `XXXX.Rmd` will be the file instructor distribute to students during the exam.  

## Download

```{r}
library(rmdgrader)
library(dplyr)
# the google drive url with students' submissions
gd_url <- "https://drive.google.com/drive/u/0/folders/1lO5s1qeGacUVE4y0hCDaHAr0-n0n6lljKEpDTsKsI9S90jNXRBvRZOV4jHgVtqhGBzy4u3Kn"
# the title of the Google classroom assignment
title= "midterm"
# local path to save the downloads
path= "MIDTERM/submissions"

# import class roster: Must contain "學號" column and a column represents student's Google classroom login email.
roster <- readRDS("/Users/martinl/Github/110-1-r4ds-management/rosterComplete.rds")
# specify the column that can identify students google classroom login email
colname_googleClassLogin="Google classroom login email (Primary one only)"

roster[[colname_googleClassLogin]] |>
  tolower() -> roster[[colname_googleClassLogin]]

download <- rmdgrader::Download(title, path)
download$get_courseWork(gd_url, roster, colname_googleClassLogin)
# download all
download$courseWork$download(overwrite = T)
```

  * The downloaded Rmds will be renamed to `title-studentIds.Rmd` 


```{r}
# download one
download$courseWork$download(validSchoolIds=410872134, overwrite = T)
download$courseWork$download(validSchoolIds=411073129, overwrite = T)
#
download$courseWork$download(validSchoolIds=411073126, overwrite = T)
```

## Process

  * In case of something unexpected happened, it would be safe to backup the downloaded Rmds somewhere else instead of keeping only one copy in the submission folder.

```{r}
library(rmdgrader)
library(purrr)
library(dplyr)
process <- rmdgrader::Process2(
  ansRmd="/Users/martinl/Github/110-1-r4ds-management/midterm-ans.Rmd",
  path_studentRmds = "MIDTERM/submissions"
)
process$correctAnsFilename$tryGet_list_codeChunks()
process$inBatch_studentsRmds$tryGet_list_codeChunks()

# saved the process stage result
process$export(path="MIDTERM")
```


## Evaluate

```{r}
library(rmdgrader)
processed <- readRDS("MIDTERM/processed.Rds")
ev <- rmdgrader::Evaluate(processed)
# For each part of the ans.Rmd, you can resolve for answer objects for grading later
ev$answerValues$batch$resolve$part1()
# save the evaluation stage result
ev$save("MIDTERM/evaluated.Rdata")

```

## Grading

```{r}
load("MIDTERM/evaluated.Rdata")
library(rmdgrader)
library(purrr)
library(dplyr)
process = readRDS("MIDTERM/processed.Rds")
ae <- allequalService2(process, path="MIDTERM/submissions")
```

  * `ae` contains all the comparison results, which are grouped and can be checked by
  
```{r}
# For ans11, check Group 1 comparison result
ae$ans11$check_messageGroups$G1()
```

  * After showing, assign grade to the group by:
  
```{r}
# if given 5 points
ae$ans11$check_messageGroups$G1grade$grade(5)
```

  * If want to put down comment, 

```{r}
ae$ans11$check_messageGroups$G1grade$comment("your comment")
```

  If want ot bring out some student's code in a group:

```{r}
ae$ans11$code$G1$`midterm-410872134.Rmd`()
```

***

After settling down with `ans11` grading, save the grade by:

```{r}
ae$save_grade$ans11()
```

  * If you want to see the saved grade, 

```{r}
ae$grades$ans11
```

The above process needs to be done for all `ans`.

## Synthesize

This is a stage to add student grade to student's Rmd file for returning purpose.

```{r}
library(rmdgrader)
df_grades = readRDS("/Users/martinl/Github/110-1-r4ds-management/MIDTERM/grades.Rds")
# define the mapping between each ansXXX and its Rmd header.
list(ans11="## 1.1", ans12="## 1.2", ans13="## 1.3", ans14="## 1.4", ans15="## 1.5") -> mapping

path="MIDTERM/submissions"
syn <- rmdgrader::Synthesize(df_grades, mapping, path)
# synthesize all Rmds
syn$all()
# synthesize one Rmd
syn$individual$`midterm-410872134.Rmd`()
```

## Inspection

  * use `rmdgrader::Inspect(path)` to initiate an inspect instance. Make sure the global environment has `df_grades` in it.
  
```{r}
library(rmdgrader)
df_grades = readRDS("/Users/martinl/Github/110-1-r4ds-management/MIDTERM/grades.Rds")
path="MIDTERM/submissions2"
isp <- rmdgrader::Inspect(path)
```

Use the following to file.edit the first Rmd
```{r}
isp$file.edit$`Finalexam-410872134.Rmd`()
```

Use the following to file.edit the next Rmd, continue to use `$file.edit_next()` for the next Rmd, `$file.edit_previous()` to go back:
```{r}
isp$file.edit_next()
```

  * When manually change grades, make sure ansXXX and total are changed accordingly in the frontmatter. They will be used to update `df_grades`

Use the following method to update the df_grades row corresponding to the Rmd file:
```{r}
isp$update_grade$`Finalexam-410872134.Rmd`()
```
  
```{r}
saveRDS(df_grades, file="/Users/martinl/Github/110-1-r4ds-management/MIDTERM/grades.Rds")
```

## Return


```{r}
source("support/main.R")
source("support/midterm.R")
library(rmdgrader)
library(dplyr)
gd_url <- "https://drive.google.com/drive/folders/1BbD2wbI4gK-14ViZnbeu5dQGTctchdSQCjD-AzcbGfmzBDeT-9poom_nOjwjtF7wcu--yOk0"
title= "Final exam" # title of google class assignment
path= "FINAL/submissions" # the local folder to download student turn ins.
roster <- readRDS("rosterComplete.rds")
colname_googleClassLogin="Google classroom login email (Primary one only)"
roster[[colname_googleClassLogin]] |>
  tolower() -> roster[[colname_googleClassLogin]]
# undebug(rmdgrader::Download)
download <- rmdgrader::Download(title, path)
download$get_courseWork(gd_url, roster, colname_googleClassLogin)
```


```{r}
rt <- rmdgrader::Return2(
  path="FINAL/submissions2",
  download=download
)
rt$return_all()
```


